---
title: "ctmle"
author: "Asantewaa"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(SuperLearner)
library(randomForest)
library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(broom)
library(MASS)  
library(boot)
library(survey)
library(tmle)
library(ctmle)
library(glm2)
library(glmnet)
set.seed(123)   
```

### Fixed Data

```{r}
fixed_data <- read.csv("data.csv")
fixed_data$X <- NULL
summary(fixed_data)
```

### Simulation Study 1: low-dimensional, highly correlated covariates

```{r}
simulation1 <- function(n=1000){
  mu <- c(0.5, 1)
  sigma <- matrix(c(2, 1, 1, 1), nrow = 2)  
  logit <- function(p) log(p / (1 - p))
  expit <- function(x) 1 / (1 + exp(-x)) 
  
  W <- mvrnorm(n, mu = mu, Sigma = sigma)
  W1 <- W[, 1]
  W2 <- W[, 2]
  g0 <- expit(0.5 + 0.25 * W1 + 0.75 * W2)
  T <- rbinom(n, 1, g0)
  
  Q0 <- 1 + T + W1 + 2 * W2
  epsilon <- rnorm(n, mean = 0, sd = 1) 
  Y <- Q0 + epsilon
  
  data1 <- data.frame(W1 = W1, W2 = W2, T = T, Y = Y)
  
  return(data1)
}
#write.csv(simulation1(), "data1.csv", row.names = FALSE)
data1 <- read.csv("data1.csv") #true value = 1
head(data1)
```

## Simulation study 2: highly correlated covariates

```{r}

simulation2 <- function(n=1000){
  W1 <- rbinom(n, 1, 0.5)
  W2 <- rbinom(n, 1, 0.5)
  W3 <- rbinom(n, 1, 0.5)
  W4 <- rbinom(n, 1, 0.2 + 0.5 * W1)
  W5 <- rbinom(n, 1, 0.05 + 0.3 * W1 + 0.1 * W2 + 0.05 * W3 + 0.4 * W4)
  W6 <- rbinom(n, 1, 0.2 + 0.6 * W5)
  W7 <- rbinom(n, 1, 0.5 + 0.2 * W3)
  W8 <- rbinom(n, 1, 0.1 + 0.2 * W2 + 0.3 * W6 + 0.1 * W7)
  
  logit_g0 <- -0.05 + 0.1 * W1 + 0.2 * W2 + 0.2 * W3 - 0.02 * W4 - 0.6 * W5 - 0.2 * W6 - 0.1 * W7
  g0 <- plogis(-logit_g0) 
  T <- rbinom(n, 1, g0)
  
  epsilon <- rnorm(n, mean = 0, sd = 1) 
  Y <- 10 + T + W1 + W2 + W4 + 2*W6+ W7 + epsilon
  
  data <- data.frame(W1, W2, W3, W4, W5, W6, W7, W8, T, Y)
  data$g0 <- g0
  
  return(data)
}

#write.csv(simulation2(), "data2.csv", row.names = FALSE)
data2 <- read.csv("data2.csv") #true value = 1
head(data2)
```

## Simulation study 3: Binary outcome with instrumental variable

```{r}
simulation3 <- function(n=1000) {
  W1 <- runif(n, 0, 1)
  W2 <- runif(n, 0, 1)
  W3 <- runif(n, 0, 1)
  W4 <- runif(n, 0, 1)
  g0_1_W <- plogis(-2 + 5 * W1 + 2 * W2 + W3) 
  
  T <- rbinom(n, size = 1, prob = g0_1_W)

  Q0 <- plogis(-3 + 2 * W2 + 2 * W3 + W4 + T)
  
  Y <- rbinom(n, size = 1, prob = Q0)
  #Y <- Q0
  
  data <- data.frame(W1, W2, W3, W4, T, Y)
  return(data)
}

#write.csv(simulation3(), "data3_binary-Y.csv", row.names = FALSE)
data3 <- read.csv("data3_binary-Y.csv") #true value = 0.2121
head(data3)
```

#### DM Estimator and Confidence Intervals

```{r}
estimate_dm <- function(data, true_value = 1) {
  treated <- data[data$T == 1, "Y"]
  control <- data[data$T == 0, "Y"]
  est <- mean(treated) - mean(control)
  se <- sqrt(var(treated) / length(treated) + var(control) / length(control))
  ci <- c(est - 1.96 * se, est + 1.96 * se)
  
  bias <- abs(est - true_value)
  MSE <- bias^2 + se^2
  list(estimate = est, bias = bias, se = se, mse = MSE, ci_lower = ci[1], ci_upper = ci[2] )
}
estimate_dm(data1)
```

#### OLS Estimator and Confidence Intervals

```{r}
estimate_ols <- function(data, true_value = 1) {
  covariates <- colnames(data)[grepl("^W", colnames(data))] 
  #formula_ols <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_ols <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  #formula_ols <-  as.formula(paste("Y ~ T + W2 +W3 + W4"))
  formula_ols <-  as.formula(paste("Y ~ T + W1 +W2"))
  #formula_ols <-  as.formula(paste("Y ~ T"))
  model <- lm(formula_ols, data = data)
  coef_est <- coef(summary(model))["T", ]
  ci <- confint(model, "T", level = 0.95)
  se <-  coef_est["Std. Error"]
  estimate <- coef_est["Estimate"]
  bias <- abs(estimate - true_value)
  MSE <- bias^2 + se^2
  
  list(estimate = estimate,bias = bias, se = se, mse = MSE, ci_lower = ci[1], ci_upper = ci[2])
}
estimate_ols(data1)
```

#### IPW Estimator and Confidence Intervals

```{r}
estimate_ipw <- function(data, true_value = 1) {
  
  covariates <- colnames(data)[grepl("^W", colnames(data))] 
  formula_ps <- as.formula(paste("T ~", paste(covariates, collapse = " + ")))  
  
  propensity_model <- glm(formula_ps, family = binomial(link = "logit"), data = data)
  
  data$weights <- ifelse(data$T == 1, 
                         1 / predict(propensity_model, type = "response", newdata = data),
                         1 / (1 - predict(propensity_model, type = "response", newdata = data)))
  
  ipw_design <- svydesign(ids = ~1, weights = ~weights, data = data)
  
  ipw_result <- svyglm(Y ~ T, design = ipw_design)
  
  coef_ipw <- coef(ipw_result)
  se_ipw <- sqrt(diag(vcov(ipw_result)))
  bias <- abs(coef_ipw["T"] - true_value)
  MSE <- bias^2 + se_ipw["T"]^2
  
  ci_ipw <- coef_ipw["T"] + c(-1.96, 1.96) * se_ipw["T"]
  list(estimate = coef_ipw["T"], 
       bias = bias,
       se = se_ipw["T"], 
       mse = MSE,
       ci_lower = ci_ipw[1], 
       ci_upper = ci_ipw[2])
}

estimate_ipw(data1)
```

The Problematic IPW

```{r}
estimate_ipw_ <- function(data, true_value = 1) {
  
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  
  count_table <- table(data$T)
  data$weights <- ifelse(
    data$T == 1,
    count_table["1"] / nrow(data),
    count_table["0"] / nrow(data)
  )
  
  formula_ipw <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + ")))
  
  ipw_design <- svydesign(ids = ~1, weights = ~weights, data = data)

  ipw_result <- svyglm(Y ~ T, design = ipw_design)
  
  coef_ipw <- coef(ipw_result)
  se_ipw <- sqrt(diag(vcov(ipw_result)))
  bias <- abs(coef_ipw["T"] - true_value)
  MSE <- bias^2 + se_ipw["T"]^2
  
  ci_ipw <- coef_ipw["T"] + c(-1.96, 1.96) * se_ipw["T"]
  list(estimate = coef_ipw["T"], 
       bias = bias,
       se = se_ipw["T"], 
       mse = MSE,
       ci_lower = ci_ipw[1], 
       ci_upper = ci_ipw[2])
}
estimate_ipw_(data1)
```

### OSE Estimator and Confidence Intervals

```{r}
estimate_ose <- function(data, true_value = 1) {
  
  
  if(all(data$Y %in% c(0, 1))){
    q_family <- binomial
  }else{
    q_family <- gaussian
  }
  
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  #formula_q <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_q <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  #formula_q <-  as.formula(paste("Y ~ T + W2 +W3 + W4"))
  formula_q <-  as.formula(paste("Y ~ T + W1 +W2"))
  Q_init <- glm(formula_q, family = q_family, data = data)
  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, data[covariates]))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, data[covariates]))
  
  formula_g <- as.formula(paste("T ~", paste(covariates, collapse = " + ")))
  g_init <- glm(formula_g, family = binomial, data = data)
  data$g1W <- predict(g_init, type = "response")
  data$g0W <- 1 - data$g1W
  
  data$H1 <- data$T / data$g1W
  data$H0 <- (1 - data$T) / data$g0W
  
  data$IF <- (data$H1 - data$H0) * (data$Y - (data$T * data$Q1W + (1 - data$T) * data$Q0W)) + (data$Q1W - data$Q0W)
  
  ATE <- mean(data$IF)
  SE <- sd(data$IF) / sqrt(nrow(data))
  CI_lower <- ATE - 1.96 * SE
  CI_upper <- ATE + 1.96 * SE
  bias <- abs(ATE - true_value)
  MSE <- bias^2 + SE^2
  
  return(list(estimate = ATE,bias = bias, se = SE, mse= MSE, ci_lower = CI_lower, ci_upper = CI_upper))
}

estimate_ose(data1)

```

### TMLE Estimator and Confidence Interval

```{r}
estimate_tmle <- function(data, true_value = 0.212, alpha = 0.05, weight = TRUE, use_single_H = FALSE, transforms = TRUE) {
  
  logit <- function(p) {
    p <- pmax(pmin(p, 0.999), 0.001)
    return(log(p / (1 - p)))
  }
  
  expit <- function(x) {
    return(1 / (1 + exp(-x)))
  }
  
  if(transforms){
    a <- min(data$Y)
    b <- max(data$Y)
    data$Y <- (data$Y - a) / (b - a)
  }
    
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  #formula_q <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_q <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  #formula_q <-  as.formula(paste("Y ~ T + W1 +W2"))
  formula_q <-  as.formula(paste("Y ~ T + W2 +W3 + W4"))
  Q_init <- glm(formula_q, family = gaussian, data = data)
  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, data[covariates]))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, data[covariates]))
  data$Q <- predict(Q_init, type = "response")
  
  formula_g <- as.formula(paste("T ~", paste(covariates, collapse = " + ")))
  g_init <- glm(formula_g, family = binomial, data = data)
  data$g1W <- predict(g_init, type = "response")
  
  data$k_Q1 <- if (weight) 1 else 1 / data$g1W
  data$k_Q0 <- if (weight) 1 else 1 / (1 - data$g1W)
  
  data$H <-if (weight) data$T - (1 - data$T) else (data$T / data$g1W) - ((1 - data$T) / (1 - data$g1W))
  data$weights_single_H <- if (weight) ifelse(data$T == 1, 1 / data$g1W, 1 / (1 - data$g1W)) else 1
  data$H1 <- if(weight) data$T else data$T / data$g1W
  data$H0 <- if(weight) (1  - data$T) else ((1 - data$T) / (1 - data$g1W))
  data$weights_H1 <- if (weight) 1 / data$g1W else 1
  data$weights_H0 <- if (weight) 1 / (1 - data$g1W) else 1

  if (use_single_H) {
    if (transforms) {
      second_stage <- glm2(data$Y ~ -1 + H + offset(logit(data$Q)), 
                           family = quasibinomial, data = data, weights = weights_single_H)
      epsilon <- coef(second_stage)[1]
      Q_star1 <- expit(logit(data$Q1W) + epsilon * data$k_Q1)
      Q_star0 <- expit(logit(data$Q0W) - epsilon * data$k_Q0)
    } else {
      second_stage <- glm2(data$Y ~ -1 + H + offset(data$Q), 
                           family = gaussian, data = data, weights = weights_single_H)
      epsilon <- coef(second_stage)[1]
      Q_star1 <- data$Q1W + epsilon * data$k_Q1
      Q_star0 <- data$Q0W - epsilon * data$k_Q0
    }
  } else {
    if (transforms) {
      second_stage_1 <- glm2(data$Y ~ -1 + H1 + offset(logit(data$Q)), 
                             family = quasibinomial, data = data, weights = weights_H1)
      second_stage_0 <- glm2(data$Y ~ -1 + H0 + offset(logit(data$Q)), 
                             family = quasibinomial, data = data, weights = weights_H0)
      epsilon_1 <- coef(second_stage_1)[1]
      epsilon_0 <- coef(second_stage_0)[1]
      Q_star1 <- expit(logit(data$Q1W) + epsilon_1 * data$k_Q1)
      Q_star0 <- expit(logit(data$Q0W) + epsilon_0 * data$k_Q0)
    } else {
      second_stage_1 <- glm2(data$Y ~ -1 + H1 + offset(data$Q), 
                             family = gaussian, data = data, weights = weights_H1)
      second_stage_0 <- glm2(data$Y ~ -1 + H0 + offset(data$Q), 
                             family = gaussian, data = data, weights = weights_H0)
      epsilon_1 <- coef(second_stage_1)[1]
      epsilon_0 <- coef(second_stage_0)[1]
      Q_star1 <- data$Q1W + epsilon_1 * data$k_Q1
      Q_star0 <- data$Q0W + epsilon_0 * data$k_Q0
    }
  }
  
  if (transforms) {
    ATE_pre <- mean(data$Q1W - data$Q0W) * (b - a)
    ATE <- mean(Q_star1 - Q_star0) * (b - a)
}else{
    ATE_pre <- mean(data$Q1W - data$Q0W)
    ATE <- mean(Q_star1 - Q_star0)
}
  
  bias <- abs(ATE - true_value)
  
  if  (transforms) {
    ATE_n <- ATE/ (b - a)
  }else{
    ATE_n <- ATE 
  }
  data$H_n <- (data$T / data$g1W) - ((1 - data$T) / (1 - data$g1W))
  data$H_1 <- data$T / data$g1W
  data$H_0 <- (1 - data$T) / (1 - data$g1W)
  
  if(use_single_H){
    IF <- data$H_n * (data$Y - (data$T * Q_star1 + (1 - data$T) * Q_star0)) + (Q_star1 - Q_star0) - ATE_n
    IF_1 <- mean(data$H_n * (data$Y - (data$T * Q_star1 + (1 - data$T) * Q_star0)))
    IF_0 <- mean((Q_star1 - Q_star0) - ATE_n)
  }else{
    IF <- data$H_1* (data$Y - Q_star1) - data$H_0 * (data$Y - Q_star0) + (Q_star1 - Q_star0) - ATE_n
    IF_1 <- mean(data$H_1* (data$Y - Q_star1) - data$H_0 * (data$Y - Q_star0))
    IF_0 <- mean((Q_star1 - Q_star0) - ATE_n)
  }
  
  
  n <- nrow(data)
  SE <- if(transforms) sqrt(var(IF) / n) * (b - a) else sqrt(var(IF) / n)
  z <- qnorm(1 - alpha / 2)
  
  CI_lower <- ATE - z * SE
  CI_upper <- ATE + z * SE
  MSE <- bias^2 + SE^2
  
  return(list(estimate = ATE, bias = bias, se = SE, mse = MSE, ci_lower = CI_lower, ci_upper = CI_upper))
}

result <- estimate_tmle(data3)
print(result)
```

```{r}
greedy_ctmle <- function(data, true_value = 1, alpha = 0.05) {
  
  logit <- function(p) {
    p <- pmax(pmin(p, 0.999), 0.001)
    return(log(p / (1 - p)))
  }
  
  expit <- function(x) {
    return(1 / (1 + exp(-x)))
  }
  
  a <- min(data$Y)
  b <- max(data$Y)
  data$Y <- (data$Y - a) / (b - a)
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  #formula_q <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_q <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  formula_q <-  as.formula(paste("Y ~ T + W1 +W2"))
  Q_init <- glm(formula_q, family = gaussian, data = data)
  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, data[covariates]))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, data[covariates]))
  data$Q <- predict(Q_init, type = "response")

  selected_vars <- c()
  remaining_vars <- covariates
  min_loss <- Inf
  best_g <- NULL
  
  for (k in 1:length(covariates)) {
    losses <- c()
    g_models <- list()
    
    for (cov_var in remaining_vars) {
      vars_to_use <- c(selected_vars, cov_var)
      formula_g <- as.formula(paste("T ~", paste(vars_to_use, collapse = " + ")))
      g_model <- glm2(formula_g, family = binomial, data = data)
      g1W <- predict(g_model, type = "response")
      
      data$H1 <- data$T 
      data$H0 <- (1 - data$T) 
      data$weights_H1 <-  1 / g1W 
      data$weights_H0 <-  1 / (1 - g1W) 
      
      second_stage_1 <- glm2(data$Y ~ -1 + H1 + offset(logit(data$Q)), family = quasibinomial, data = data, weights = weights_H1)
      second_stage_0 <- glm2(data$Y ~ -1 + H0 + offset(logit(data$Q)), family = quasibinomial, data = data, weights = weights_H0)
      epsilon_1 <- coef(second_stage_1)[1]
      epsilon_0 <- coef(second_stage_0)[1]
      Q_star1 <- expit(logit(data$Q1W) + epsilon_1 )
      Q_star0 <- expit(logit(data$Q0W) + epsilon_0 )
      
      loss <- mean((data$Y - (data$T * Q_star1 + (1 - data$T) * Q_star0))^2)
      losses <- c(losses, loss)
      
      g_models[[cov_var]] <- list(g_model = g_model, loss = loss, g1W = g1W,
                                  epsilon_1 = epsilon_1, epsilon_0 = epsilon_0,
                                  Q_star1 = Q_star1, Q_star0 = Q_star0)
      
      #cat("\nIteration:", k, "| Testing Combination:", paste(vars_to_use, collapse = " + "), "| Loss:", loss, "\n")
    }
    best_var <- remaining_vars[which.min(losses)]
    best_model <- g_models[[best_var]]
    
    if (best_model$loss < min_loss) {
      min_loss <- best_model$loss
      selected_vars <- c(selected_vars, best_var)
      remaining_vars <- setdiff(remaining_vars, best_var)
      best_g <- best_model$g_model
      best_g1W <- best_model$g1W
      epsilon_1 <- best_model$epsilon_1
      epsilon_0 <- best_model$epsilon_0
      Q_star1 <- best_model$Q_star1
      Q_star0 <- best_model$Q_star0
      best_combination <- selected_vars
      
      #cat("Selected combination so far:", paste(selected_vars, collapse = " + "), "| Updated min loss:", min_loss, "\n")
    } else {
      #cat("No improvement in loss, stopping selection.\n")
      break
    }
  }
  
  cat("\nBest combination chosen:", paste(best_combination, collapse = " + "), "\n")
  
  ATE_pre <- mean(data$Q1W - data$Q0W) * (b - a)
  ATE <- mean(Q_star1 - Q_star0) * (b - a)
  ATE_n <- ATE/(b - a)
  
  data$H_1 <- data$T / best_g1W
  data$H_0 <- (1 - data$T) / (1 - best_g1W)
  IF <- (data$T / best_g1W) * (data$Y - Q_star1) - ((1 - data$T) / (1 - best_g1W)) * (data$Y - Q_star0) + (Q_star1 - Q_star0) - ATE_n
  
  IF_1 <- mean((data$T / best_g1W) * (data$Y - Q_star1) - ((1 - data$T) / (1 - best_g1W)) * (data$Y - Q_star0))
  IF_0 <- mean((Q_star1 - Q_star0) - ATE_n)
  SE <- sqrt(var(IF) / nrow(data))
  z <- qnorm(1 - alpha / 2)
  CI_lower <- ATE - z * SE
  CI_upper <- ATE + z * SE
  bias <- abs(ATE - true_value)
  MSE <- bias^2 + SE^2
  
  
  return(list(estimate = ATE, bias = bias, se = SE, mse = MSE, ci_lower = CI_lower, ci_upper = CI_upper))
}

greedy_ctmle(data1)

```

```{r}
sl_ctmle <- function(data, true_value = 1, alpha = 0.05) {
  
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  #formula_q <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_q <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  #formula_q <-  as.formula(paste("Y ~ T + W2 +W3 + W4"))
  formula_q <-  as.formula(paste("Y ~ T + W1 +W2"))
  #formula_q <-  as.formula(paste("Y ~ T"))
  Q_init <- glm(formula_q, family = gaussian, data = data)
  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, data[covariates]))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, data[covariates]))
  data$Q <- predict(Q_init, type = "response")

  SL.library <- c("SL.glm", "SL.glmnet", "SL.randomForest", "SL.gam")
  X <- data[, covariates]
  Y_T <- data$T
  
  g_superlearner <- SuperLearner(Y = Y_T, X = X, family = binomial, SL.library = SL.library)
  data$g1W <- g_superlearner$SL.predict

  data$H1 <- data$T / data$g1W
  data$H0 <- (1 - data$T) / (1 - data$g1W)
  
  second_stage_1 <- glm(data$Y ~ -1 + H1 + offset(data$Q), family = gaussian, data = data)
  epsilon_1 <- coef(second_stage_1)[1]
  second_stage_0 <- glm(data$Y ~ -1 + H0 + offset(data$Q), family = gaussian, data = data)
  epsilon_0 <- coef(second_stage_0)[1]
  
  Q_star1 <- data$Q1W + epsilon_1 * (1 / data$g1W)
  Q_star0 <- data$Q0W + epsilon_0 * (1 / (1 - data$g1W))

  ATE <- mean(Q_star1 - Q_star0)
  IF <- data$H1 * (data$Y - Q_star1) - data$H0 * (data$Y - Q_star0) + (Q_star1 - Q_star0) - ATE
  SE <- sqrt(var(IF) / nrow(data))
  z <- qnorm(1 - alpha / 2)
  CI_lower <- ATE - z * SE
  CI_upper <- ATE + z * SE
  bias <- abs(ATE - true_value)
  MSE <- bias^2 + SE^2
  
  print(mean(data$Q1W - data$Q0W))
  return(list(estimate = ATE, bias = bias, se = SE, mse = MSE, ci_lower = CI_lower, ci_upper = CI_upper))
}


sl_ctmle(data1)

```

```{r}
ctmle1 <- function(data, true_value = 1, alpha = 0.05) {
  
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  
  
  #formula_q <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_q <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  #formula_q <-  as.formula(paste("Y ~ T + W2 +W3 + W4"))
  formula_q <-  as.formula(paste("Y ~ T + W1 +W2"))
  #formula_q <-  as.formula(paste("Y ~ T"))
  Q_init <- glm(formula_q, family = gaussian, data = data)
  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, data[covariates]))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, data[covariates]))
  data$Q <- predict(Q_init, type = "response")
  
  formula_g <- paste("T ~", paste(covariates, collapse = " + "))
  x <- model.matrix(as.formula(formula_g), data = data)
  y <- data$T
  
  cv_glmnet <- cv.glmnet(x, y, alpha = 1, family = "binomial")
  lambda_seq <- cv_glmnet$lambda 
  best_lambda <- NULL
  min_loss <- Inf
  
  for (lambda in lambda_seq) {
    g_model <- glmnet(x, y, alpha = 1, family = "binomial", lambda = lambda)
    g1W <- as.numeric(predict(g_model, newx = x, type = "response"))  
    
    data$H1 <- data$T / g1W
    data$H0 <- (1 - data$T) / (1 - g1W)
  
    second_stage <- glm(data$Y ~ -1 + H1 + H0 + offset(data$Q), family = gaussian, data = data)
    epsilon <- as.numeric(coef(second_stage))  
    data$Q_star1 <- data$Q1W + epsilon[1] / g1W
    data$Q_star0 <- data$Q0W - epsilon[1] / (1 - g1W)
    
    loss <- mean((data$Y - (data$T * data$Q_star1 + (1 - data$T) * data$Q_star0))^2)
    
    if (loss < min_loss) {
      min_loss <- loss
      best_lambda <- lambda
      best_g1W <- g1W
      Q_star1 <- data$Q_star1
      Q_star0 <- data$Q_star0
    }
  }
  
  c <- coef(g_model, s =best_lambda)

  ATE_pre <- mean(data$Q1W - data$Q0W)
  ATE <- mean(Q_star1 - Q_star0)
  IF <- (data$T / best_g1W) * (data$Y - Q_star1) - ((1 - data$T) / (1 - best_g1W)) * (data$Y - Q_star0) + (Q_star1 - Q_star0) - ATE
  SE <- sqrt(var(IF) / nrow(data))
  z <- qnorm(1 - alpha / 2)
  CI_lower <- ATE - z * SE
  CI_upper <- ATE + z * SE
  bias <- abs(ATE - true_value)
  MSE <- bias^2 + SE^2
  print(ATE_pre)
  
  return(list(
    estimate = unname(ATE),
    bias = unname(bias),
    se = unname(SE),
    #coef = c,
    mse = unname(MSE),
    ci_lower = unname(CI_lower),
    ci_upper = unname(CI_upper),
    best_lambda = best_lambda
  ))
}

ctmle1(data1)
```

```{r}
ctmle0 <- function(data, true_value = 1, alpha = 0.05) {
  
  covariates <- colnames(data)[grepl("^W", colnames(data))]
  
  #formula_q <- as.formula(paste("Y ~ T +", paste(covariates, collapse = " + "), "+ T:(", paste(covariates, collapse = " + "), ")"))
  #formula_q <- as.formula(paste("Y ~ T + W1 + W2 + W4 + W6+ W7"))
  #formula_q <-  as.formula(paste("Y ~ T + W2 +W3 + W4"))
  formula_q <-  as.formula(paste("Y ~ T + W1 +W2"))
  #formula_q <-  as.formula(paste("Y ~ T"))
  Q_init <- glm(formula_q, family = gaussian, data = data)
  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, data[covariates]))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, data[covariates]))
  data$Q <- predict(Q_init, type = "response")

  formula_g <- paste("T ~", paste(covariates, collapse = " + "))
  x <- model.matrix(as.formula(formula_g), data = data)
  y <- data$T

  cv_glmnet <- cv.glmnet(x, y, alpha = 1, family = "binomial")
  lambda_seq <- cv_glmnet$lambda

  best_lambda <- NULL
  min_loss <- Inf
  best_g1W <- NULL
  best_Q_star1 <- NULL
  best_Q_star0 <- NULL

  for (lambda in lambda_seq) {
    g_model <- glmnet(x, y, alpha = 1, family = "binomial", lambda = lambda)
    g1W <- as.numeric(predict(g_model, newx = x, type = "response"))  

    data$H <- data$T / g1W -((1 - data$T) / (1 - g1W))
    
    g_grad <- predict(g_model, newx = x, type = "link", s = lambda, exact = TRUE, grad = TRUE)
    data$H_grad <- (1 - data$T) / (1 - g1W)^2 * (-g_grad) + data$T / g1W^2 * g_grad

    second_stage <- glm(data$Y ~ -1 + H + H_grad + offset(data$Q), family = gaussian, data = data)
    epsilon <- as.numeric(coef(second_stage)) 
    data$Q_star1 <- data$Q1W + epsilon[1] / g1W + (epsilon[2]/ g1W^2) * g_grad
    data$Q_star0 <- data$Q0W - epsilon[1] / (1 - g1W) + (epsilon[2]/ (1 - g1W)^2) * (-g_grad)
   
    loss <- mean((data$Y - (data$T * data$Q_star1 + (1 - data$T) * data$Q_star0))^2) 
 
    if (loss < min_loss) {
      min_loss <- loss
      best_lambda <- lambda
      best_g1W <- g1W
      Q_star1 <- data$Q_star1
      Q_star0 <- data$Q_star0
    }
  }
  
  c <- coef(g_model, s =best_lambda)

  ATE_pre <- mean(data$Q1W - data$Q0W)
  ATE <- mean(Q_star1 - Q_star0)
  IF <- (data$T / best_g1W) * (data$Y - Q_star1) - ((1 - data$T) / (1 - best_g1W)) * (data$Y - Q_star0) + (Q_star1 - Q_star0) - ATE
  SE <- sqrt(var(IF) / nrow(data))
  z <- qnorm(1 - alpha / 2)
  CI_lower <- ATE - z * SE
  CI_upper <- ATE + z * SE
  bias <- abs(ATE - true_value)
  MSE <- bias^2 + SE^2

  return(list(
    estimate = unname(ATE),
    bias = unname(bias),
    se = unname(SE),
    coef = c,
    mse = unname(MSE),
    ci_lower = unname(CI_lower),
    ci_upper = unname(CI_upper),
    best_lambda = best_lambda
  ))
}

ctmle0(data1)
```

### TMLE & CTMLE Packages

```{r}
estimate_tmle_package <- function(data) {
  covariates <- c(colnames(data)[grepl("^W", colnames(data))])
  W <- as.matrix(data[, covariates])
  result <- tmle(
    Y = data$Y, 
    A = data$T, 
    W = W, 
    Qform = "Y~A+W1+W2",  
    gform = "A~W1+W2",              
    family = "gaussian",         
    verbose = FALSE
  )
  
  ATE_tmle <- result$estimates$ATE$psi
  SE_tmle <- result$estimates$ATE$var.psi^0.5
  CI_tmle <- result$estimates$ATE$CI
  bias_tmle <- abs(ATE_tmle - 1)
  MSE <- bias_tmle^2 + SE_tmle^2
  
  return(list(estimate = ATE_tmle, bias = bias_tmle, se = SE_tmle, mse = MSE, ci_lower = CI_tmle[1], ci_upper = CI_tmle[2]))
}

estimate_tmle_package(data1)
```

```{r}
tmle_ <- tmle(Y = data1$Y, A = data1$T, W = W,Q.SL.library = "SL.glm",g.SL.library = "SL.glm",g.Delta.SL.library =  "SL.glm", family = "gaussian" )

summary(tmle_)
```

### Visualization

```{r}
estimators <- list(
  DM = estimate_dm,
  OLS = estimate_ols,
  IPW = estimate_ipw,
  IPW_Alternative = estimate_ipw_,
  OSE = estimate_ose,
  TMLE = estimate_tmle,
  TMLE_PACKAGE = estimate_tmle_package,
  Greedy_CTMLE = greedy_ctmle,
  SL_CTMLE = sl_ctmle,
  LASSO_CTMLE1 = ctmle1,
  LASSO_CTMLE0 = ctmle0
)

evaluate_estimators <- function(data) {
  results <- list()
  
  for (name in names(estimators)) {
    estimator <- estimators[[name]]
    
    result <- estimator(data)
    
    results[[name]] <- data.frame(
      Estimate = if ("estimate" %in% names(result)) result$estimate else NA,
      SE = if ("se" %in% names(result)) result$se else NA,
      CI_Lower = if ("ci_lower" %in% names(result)) result$ci_lower else NA,
      CI_Upper = if ("ci_upper" %in% names(result)) result$ci_upper else NA,
      Bias = if ("bias" %in% names(result)) result$bias else NA,
      MSE = if ("mse" %in% names(result)) result$mse else NA
    )
  }
  
  results_df <- do.call(rbind, results)
  results_df$Algorithm <- rownames(results_df)
  rownames(results_df) <- NULL 
  results_df <- results_df[, c("Algorithm", "Estimate", "SE", "CI_Lower", "CI_Upper", "Bias", "MSE")]
  return(results_df)
}

results_table <- evaluate_estimators(data1)
print(results_table)
```

```{r}
print(colnames(results_table))

```

```{r}
results_table$Algorithm <- factor(results_table$Algorithm, levels = rev(results_table$Algorithm))

true_value <- 1
ggplot(results_table, aes(x = Algorithm, y = Estimate)) +
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), width = 0.2) + 
  geom_hline(yintercept = true_value, color = "green", linetype = "dashed") +  
  coord_flip() +  
  labs(
    title = "ATE Estimates by Algorithm",
    x = "Algorithm",
    y = "Estimates"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14)
  )

```

```{r}
library(viridis)

true_value <- 1

ggplot(results_table, aes(x = Algorithm, y = Estimate)) +
  geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper, color = Algorithm), width = 0.2, show.legend = FALSE) + geom_point(size = 3) +
  geom_hline(yintercept = true_value, color = "black", linetype = "dashed") +  
  coord_flip() +  
  labs(
    title = expression(paste("Well-specified model for ", bar(Q)[0])),
    x = "Algorithm",
    y = "Estimates"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14)
  ) +
  scale_color_viridis_d() 


```
